### 2023-01-17 sections/experiments/mitigation_strategies.qmd

include("src/setup.jl")
eval(setup)
output_path = output_dir("mitigation_strategies")
www_path = www_dir("mitigation_strategies")
```

@@

@@

choices = [
    :linearly_separable, 
    :overlapping, 
    :circles, 
    :moons,
]
img_files = readdir(www_path)[contains.(readdir(www_path),"line_chart") .&& .!contains.(readdir(www_path),"latent")]
img_files = img_files[Bool.(reduce(+, map(choice -> contains.(img_files, string(choice)), choices)))]
img_files = joinpath.(www_path,img_files)
for img in img_files
    display(load(img))
end
```

@@

choices = [
    :linearly_separable, 
    :overlapping, 
    :circles, 
    :moons,
]
img_files = readdir(www_path)[contains.(readdir(www_path),"errorbar_chart") .&& .!contains.(readdir(www_path),"latent")]
img_files = img_files[Bool.(reduce(+, map(choice -> contains.(img_files, string(choice)), choices)))]
img_files = joinpath.(www_path,img_files)
for img in img_files
    display(load(img))
end
```

@@

@@

```{julia}
using DataFrames, Statistics
df = results[:overlapping].output
df = df[df.n .== maximum(df.n),:]
gdf = groupby(df, [:generator, :model, :n, :name, :scope])
df_plot = combine(gdf, :value => (x -> [(mean(x),mean(x)+std(x),mean(x)-std(x))]) => [:mean, :ymax, :ymin])
df_plot = df_plot[[name in [:mmd, :mmd_grid, :model_performance] for name in df_plot.name],:]
df_plot = df_plot[.!(df_plot.name.==:mmd .&& df_plot.scope.==:model),:]
df_plot = mapcols(x -> typeof(x) == Vector{Symbol} ? string.(x) : x, df_plot)
transform!(df_plot, :name => (X -> [x=="mmd" ? "MMD (domain)" : x for x in X]) => :name)
transform!(df_plot, :name => (X -> [x=="mmd_grid" ? "MMD (model)" : x for x in X]) => :name)
transform!(df_plot, :name => (X -> [x=="model_performance" ? "Performance" : x for x in X]) => :name)
transform!(df_plot, :generator => (X -> [x=="Generic" ? "Generic (γ=0.5)" : x for x in X]) => :generator)
transform!(df_plot, :generator => (X -> [x=="Generic_conservative" ? "Generic (γ=0.9)" : x for x in X]) => :generator)
transform!(df_plot, :model => (X -> [x=="FluxEnsemble" ? "Deep Ensemble" : x for x in X]) => :model)
transform!(df_plot, :model => (X -> [x=="FluxModel" ? "MLP" : x for x in X]) => :model)
transform!(df_plot, :model => (X -> [x=="LogisticRegression" ? "Linear" : x for x in X]) => :model)

@@

img_files = readdir(www_path)[contains.(readdir(www_path),"line_chart") .&& contains.(readdir(www_path),"latent")]
img_files = joinpath.(www_path,img_files)
for img in img_files
    display(load(img))
end
```

@@

img_files = readdir(www_path)[contains.(readdir(www_path),"errorbar_chart") .&& contains.(readdir(www_path),"latent")]
img_files = joinpath.(www_path,img_files)
for img in img_files
    display(load(img))
end
```

@@

```{julia}
using DataFrames, Statistics
df = results[:overlapping].output
df = df[df.n .== maximum(df.n),:]
gdf = groupby(df, [:generator, :model, :n, :name, :scope])
df_plot = combine(gdf, :value => (x -> [(mean(x),mean(x)+std(x),mean(x)-std(x))]) => [:mean, :ymax, :ymin])
df_plot = df_plot[[name in [:mmd, :mmd_grid, :model_performance] for name in df_plot.name],:]
df_plot = df_plot[.!(df_plot.name.==:mmd .&& df_plot.scope.==:model),:]
df_plot = mapcols(x -> typeof(x) == Vector{Symbol} ? string.(x) : x, df_plot)
transform!(df_plot, :name => (X -> [x=="mmd" ? "MMD (domain)" : x for x in X]) => :name)
transform!(df_plot, :name => (X -> [x=="mmd_grid" ? "MMD (model)" : x for x in X]) => :name)
transform!(df_plot, :name => (X -> [x=="model_performance" ? "Performance" : x for x in X]) => :name)
transform!(df_plot, :generator => (X -> [x=="Latent" ? "Latent (γ=0.5)" : x for x in X]) => :generator)
transform!(df_plot, :generator => (X -> [x=="Latent_conservative" ? "Latent (γ=0.9)" : x for x in X]) => :generator)
transform!(df_plot, :model => (X -> [x=="FluxEnsemble" ? "Deep Ensemble" : x for x in X]) => :model)
transform!(df_plot, :model => (X -> [x=="FluxModel" ? "MLP" : x for x in X]) => :model)
transform!(df_plot, :model => (X -> [x=="LogisticRegression" ? "Linear" : x for x in X]) => :model)

@@

Images.load(joinpath(www_path,"paper_synthetic_latent_results.png"))
```

@@

choices = [
    :cal_housing, 
    :credit_default, 
    :gmsc, 
]
img_files = readdir(www_path)[contains.(readdir(www_path),"line_chart")]
img_files = img_files[Bool.(reduce(+, map(choice -> contains.(img_files, string(choice)), choices)))]
img_files = joinpath.(www_path,img_files)
for img in img_files
    display(load(img))
end
```

@@

choices = [
    :cal_housing, 
    :credit_default, 
    :gmsc, 
]
img_files = readdir(www_path)[contains.(readdir(www_path),"errorbar_chart")]
img_files = img_files[Bool.(reduce(+, map(choice -> contains.(img_files, string(choice)), choices)))]
img_files = joinpath.(www_path,img_files)
for img in img_files
    display(load(img))
end
```

@@

@@

```{julia}
using DataFrames, Statistics
model_ = :FluxModel
df = DataFrame() 
for (key, val) in results
    df_ = deepcopy(val.output)
    df_.dataset .= key
    df = vcat(df,df_)
end
df = df[df.n .== maximum(df.n),:]
df = df[df.model .== model_,:]
filter!(:value => x -> !any(f -> f(x), (ismissing, isnothing, isnan)), df)
gdf = groupby(df, [:generator, :dataset, :n, :name, :scope])
df_plot = combine(gdf, :value => (x -> [(mean(x),mean(x)+std(x),mean(x)-std(x))]) => [:mean, :ymax, :ymin])
df_plot = df_plot[[name in [:mmd, :model_performance] for name in df_plot.name],:]
df_plot = df_plot[.!(df_plot.name.==:mmd .&& df_plot.scope.!=:model),:]
df_plot = mapcols(x -> typeof(x) == Vector{Symbol} ? string.(x) : x, df_plot)
transform!(df_plot, :dataset => (X -> [x=="cal_housing" ? "California Housing" : x for x in X]) => :dataset)
transform!(df_plot, :dataset => (X -> [x=="credit_default" ? "Credit Default" : x for x in X]) => :dataset)
transform!(df_plot, :dataset => (X -> [x=="gmsc" ? "GMSC" : x for x in X]) => :dataset)
transform!(df_plot, :name => (X -> [x=="mmd" ? "MMD (model)" : x for x in X]) => :name)
transform!(df_plot, :name => (X -> [x=="model_performance" ? "Performance" : x for x in X]) => :name)
transform!(df_plot, :generator => (X -> [x=="Generic" ? "Generic (γ=0.5)" : x for x in X]) => :generator)
transform!(df_plot, :generator => (X -> [x=="Generic_conservative" ? "Generic (γ=0.9)" : x for x in X]) => :generator)

>>>>

include("src/setup.jl")
eval(setup)
output_path = output_dir("mitigation_strategies")
www_path = www_dir("mitigation_strategies")

# Artifacts:
# Images:
artifact_name = create_artifact_name_from_path(www_path, nothing)
_hash = artifact_hash(artifact_name, artifact_toml)
www_artifact_path = joinpath(artifact_path(_hash), artifact_name)
# Output:
artifact_name = create_artifact_name_from_path(output_path, nothing)
_hash = artifact_hash(artifact_name, artifact_toml)
output_artifact_path = joinpath(artifact_path(_hash), artifact_name)
```

@@

```{julia}

counterfactual_data = data_sets[:linearly_separable]
M = AlgorithmicRecourseDynamics.Models.FluxModel(counterfactual_data)
M = AlgorithmicRecourseDynamics.Models.train(M, counterfactual_data)

# Generators:
generators = Dict(
    "Generic (γ=0.5)" => GenericGenerator(opt = opt, decision_threshold=0.5),
    "Generic (γ=0.9)" => GenericGenerator(opt = opt, decision_threshold=0.9),
    "Gravitational" => GravitationalGenerator(opt = opt),
    "ClaPROAR" => ClapROARGenerator(opt = opt)
)

# Counterfactuals
x = select_factual(counterfactual_data, rand(1:size(counterfactual_data.X,2))) 
y = round(probs(M, x)[1])
target = ifelse(y==1.0,0.0,1.0) # opposite label as target
T = 50
counterfactuals = Dict([name => generate_counterfactual(x, target, counterfactual_data, M, gen; T=T, latent_space=false) for (name, gen) in generators])

# Plots:
plts = []
for (name,ce) ∈ counterfactuals
    plt = plot(ce; title=name, colorbar=false, ticks = false, legend=false, zoom=0)
    plts = vcat(plts..., plt)
end
plt = plot(plts..., size=(750,200), layout=(1,4))
savefig(plt, "paper/www/mitigation.png")
```

@@

choices = [
    :linearly_separable, 
    :overlapping, 
    :circles, 
    :moons,
]
img_files = readdir(www_artifact_path)[contains.(readdir(www_artifact_path),"line_chart") .&& .!contains.(readdir(www_artifact_path),"latent")]
img_files = img_files[Bool.(reduce(+, map(choice -> contains.(img_files, string(choice)), choices)))]
img_files = joinpath.(www_artifact_path,img_files)
for img in img_files
    display(load(img))
end
```

@@

choices = [
    :linearly_separable, 
    :overlapping, 
    :circles, 
    :moons,
]
img_files = readdir(www_artifact_path)[contains.(readdir(www_artifact_path),"errorbar_chart") .&& .!contains.(readdir(www_artifact_path),"latent")]
img_files = img_files[Bool.(reduce(+, map(choice -> contains.(img_files, string(choice)), choices)))]
img_files = joinpath.(www_artifact_path,img_files)
for img in img_files
    display(load(img))
end
```

@@

```{julia}
#| output: true
#| eval: true
#| echo: false

_file = readdir(output_artifact_path)[contains.(readdir(output_artifact_path),"bootstrap_synthetic")]
_file = joinpath.(output_artifact_path, _file)
df = CSV.File(_file) |> DataFrame
df = df[.!(ismissing.(df.p_value)),:]
df = combine(groupby(df, [:name, :scope, :data, :model, :generator]), :p_value => mean)
ENV["LINES"] = size(df, 1)
pretty_table(df)
```

@@

using DataFrames, Statistics
df = results[:overlapping].output
df = df[df.n .== maximum(df.n),:]
gdf = groupby(df, [:generator, :model, :n, :name, :scope])
df_plot = combine(gdf, :value => (x -> [(mean(x),mean(x)+std(x),mean(x)-std(x))]) => [:mean, :ymax, :ymin])
df_plot = df_plot[[name in [:mmd, :mmd_grid, :model_performance] for name in df_plot.name],:]
df_plot = df_plot[.!(df_plot.name.==:mmd .&& df_plot.scope.==:model),:]
df_plot = mapcols(x -> typeof(x) == Vector{Symbol} ? string.(x) : x, df_plot)
transform!(df_plot, :name => (X -> [x=="mmd" ? "MMD (domain)" : x for x in X]) => :name)
transform!(df_plot, :name => (X -> [x=="mmd_grid" ? "MMD (model)" : x for x in X]) => :name)
transform!(df_plot, :name => (X -> [x=="model_performance" ? "Performance" : x for x in X]) => :name)
transform!(df_plot, :generator => (X -> [x=="Generic" ? "Generic (γ=0.5)" : x for x in X]) => :generator)
transform!(df_plot, :generator => (X -> [x=="Generic_conservative" ? "Generic (γ=0.9)" : x for x in X]) => :generator)
transform!(df_plot, :model => (X -> [x=="FluxEnsemble" ? "Deep Ensemble" : x for x in X]) => :model)
transform!(df_plot, :model => (X -> [x=="FluxModel" ? "MLP" : x for x in X]) => :model)
transform!(df_plot, :model => (X -> [x=="LogisticRegression" ? "Linear" : x for x in X]) => :model)

@@

img_files = readdir(www_artifact_path)[contains.(readdir(www_artifact_path),"line_chart") .&& contains.(readdir(www_artifact_path),"latent")]
img_files = joinpath.(www_artifact_path,img_files)
for img in img_files
    display(load(img))
end
```

@@

img_files = readdir(www_artifact_path)[contains.(readdir(www_artifact_path),"errorbar_chart") .&& contains.(readdir(www_artifact_path),"latent")]
img_files = joinpath.(www_artifact_path,img_files)
for img in img_files
    display(load(img))
end
```

@@

using DataFrames, Statistics
df = results[:overlapping].output
df = df[df.n .== maximum(df.n),:]
gdf = groupby(df, [:generator, :model, :n, :name, :scope])
df_plot = combine(gdf, :value => (x -> [(mean(x),mean(x)+std(x),mean(x)-std(x))]) => [:mean, :ymax, :ymin])
df_plot = df_plot[[name in [:mmd, :mmd_grid, :model_performance] for name in df_plot.name],:]
df_plot = df_plot[.!(df_plot.name.==:mmd .&& df_plot.scope.==:model),:]
df_plot = mapcols(x -> typeof(x) == Vector{Symbol} ? string.(x) : x, df_plot)
transform!(df_plot, :name => (X -> [x=="mmd" ? "MMD (domain)" : x for x in X]) => :name)
transform!(df_plot, :name => (X -> [x=="mmd_grid" ? "MMD (model)" : x for x in X]) => :name)
transform!(df_plot, :name => (X -> [x=="model_performance" ? "Performance" : x for x in X]) => :name)
transform!(df_plot, :generator => (X -> [x=="Latent" ? "Latent (γ=0.5)" : x for x in X]) => :generator)
transform!(df_plot, :generator => (X -> [x=="Latent_conservative" ? "Latent (γ=0.9)" : x for x in X]) => :generator)
transform!(df_plot, :model => (X -> [x=="FluxEnsemble" ? "Deep Ensemble" : x for x in X]) => :model)
transform!(df_plot, :model => (X -> [x=="FluxModel" ? "MLP" : x for x in X]) => :model)
transform!(df_plot, :model => (X -> [x=="LogisticRegression" ? "Linear" : x for x in X]) => :model)

@@

Images.load(joinpath(www_artifact_path,"paper_synthetic_latent_results.png"))
```

@@

choices = [
    :cal_housing, 
    :credit_default, 
    :gmsc, 
]
img_files = readdir(www_artifact_path)[contains.(readdir(www_artifact_path),"line_chart")]
img_files = img_files[Bool.(reduce(+, map(choice -> contains.(img_files, string(choice)), choices)))]
img_files = joinpath.(www_artifact_path,img_files)
for img in img_files
    display(load(img))
end
```

@@

choices = [
    :cal_housing, 
    :credit_default, 
    :gmsc, 
]
img_files = readdir(www_artifact_path)[contains.(readdir(www_artifact_path),"errorbar_chart")]
img_files = img_files[Bool.(reduce(+, map(choice -> contains.(img_files, string(choice)), choices)))]
img_files = joinpath.(www_artifact_path,img_files)
for img in img_files
    display(load(img))
end
```

@@

```{julia}
#| output: true
#| eval: true
#| echo: false

_file = readdir(output_artifact_path)[contains.(readdir(output_artifact_path),"bootstrap_real_world")]
_file = joinpath.(output_artifact_path, _file)
df = CSV.File(_file) |> DataFrame
df = df[.!(ismissing.(df.p_value)),:]
df = combine(groupby(df, [:name, :scope, :data, :model, :generator]), :p_value => mean)
ENV["LINES"] = size(df, 1)
pretty_table(df)
```

@@

@fig-mit-real-paper shows the chart that went into the paper.

using DataFrames, Statistics
model_ = :FluxModel
df = DataFrame() 
for (key, val) in results
    df_ = deepcopy(val.output)
    df_.dataset .= key
    df = vcat(df,df_)
end
df = df[df.n .== maximum(df.n),:]
df = df[df.model .== model_,:]
filter!(:value => x -> !any(f -> f(x), (ismissing, isnothing, isnan)), df)
gdf = groupby(df, [:generator, :dataset, :n, :name, :scope])
df_plot = combine(gdf, :value => (x -> [(mean(x),mean(x)+std(x),mean(x)-std(x))]) => [:mean, :ymax, :ymin])
df_plot = df_plot[[name in [:mmd, :model_performance] for name in df_plot.name],:]
df_plot = df_plot[.!(df_plot.name.==:mmd .&& df_plot.scope.!=:model),:]
df_plot = mapcols(x -> typeof(x) == Vector{Symbol} ? string.(x) : x, df_plot)
transform!(df_plot, :dataset => (X -> [x=="cal_housing" ? "California Housing" : x for x in X]) => :dataset)
transform!(df_plot, :dataset => (X -> [x=="credit_default" ? "Credit Default" : x for x in X]) => :dataset)
transform!(df_plot, :dataset => (X -> [x=="gmsc" ? "GMSC" : x for x in X]) => :dataset)
transform!(df_plot, :name => (X -> [x=="mmd" ? "MMD (model)" : x for x in X]) => :name)
transform!(df_plot, :name => (X -> [x=="model_performance" ? "Performance" : x for x in X]) => :name)
transform!(df_plot, :generator => (X -> [x=="Generic" ? "Generic (γ=0.5)" : x for x in X]) => :generator)
transform!(df_plot, :generator => (X -> [x=="Generic_conservative" ? "Generic (γ=0.9)" : x for x in X]) => :generator)
